Order is half of life -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved More Efficiently)

### 2022-11-30 paper/03--linearization-ground.tex
some changes

Having presented the approaches for inferring preconditions and effects of compound tasks, we move on to introduce how to linearize a method's task network on top of this information. In particular, we could now view each compound task in the task network to be linearized as an ``action'' (because it is equipped with the inferred precondition and effects just as an action), and thus we could interpret the linearization problem as the problem of finding an executable linearization of a task network consisting solely of actions.

>>>>

We now move on to introduce how to linearize a method's task network. Bearing the inferred preconditions and effects of the compound tasks in a task network, we could phrase this task as follows. Given a task network $tn = (T, \parOrd{}, \alpha)$, we want to find a linearization $\langle t_{1} \cdots t_{|T|} \rangle$ of $tn$ respecting $\parOrd{}$ such that there exists a state sequence $\langle s_{1} \cdots s_{|T| - 1} \rangle$ in which $s_{1} = \effPosExt{\alpha(t_{1})}$, and for each $1 \leq i \leq |T| - 1$, $\preCondExt{t_{i + 1}} \subseteq s_{i}$ and $s_{i} \to_{\alpha(t_{i + 1})} s_{i + 1}$, namely we can view each compound task as an ``action'' and interpret the linearization problem as the problem of finding an \emph{executable} linearization of a task network consisting solely of actions.
